Practice Problems

### 2023-09-28 Stats Rethinking/Ch7/Practice Problems.qmd
Updated Prac Problems
Update Practice Problems.qmd

>>>>

```{r}
#Load his data on cars and create model with "quap"
data(cars)
m <- quap(
  alist(
    dist ~ dnorm(mu,sigma),
    mu <- a + b*speed,
    a ~ dnorm(0,100),
    b ~ dnorm(0,10),
    sigma ~ dexp(1)
  ) , data=cars )
set.seed(94)
post <- extract.samples(m,n=1000)
```

```{r}
n_samples <- 1000
logprob <- sapply( 1:n_samples ,
  function(s) {
    mu <- post$a[s] + post$b[s]*cars$speed
    dnorm( cars$dist , mu , post$sigma[s] , log=TRUE )
  } )

n_cases <- nrow(cars)
lppd <- sapply( 1:n_cases , function(i) log_sum_exp(logprob[i,]) - log(n_samples) )

pWAIC <- sapply( 1:n_cases , function(i) var(logprob[i,]) )

sum(pWAIC)
```

```{r}
lm(data=cars, dist ~ speed) %>% 
  summary()
```

```{r}
m <- quap(
  alist(
    dist ~ dnorm(mu,sigma),
    mu <- a + b*speed,
    a ~ dnorm(-17.6, 1),
    b ~ dnorm(3.9,0.1),
    sigma ~ dnorm(15,2)
  ) , data=cars )
set.seed(94)
post <- extract.samples(m,n=1000)

n_samples <- 1000
logprob <- sapply( 1:n_samples ,
  function(s) {
    mu <- post$a[s] + post$b[s]*cars$speed
    dnorm( cars$dist , mu , post$sigma[s] , log=TRUE )
  } )

n_cases <- nrow(cars)
lppd <- sapply( 1:n_cases , function(i) log_sum_exp(logprob[i,]) - log(n_samples) )

pWAIC <- sapply( 1:n_cases , function(i) var(logprob[i,]) )

sum(pWAIC)
```
